AHABus \& FCORE:\\Modular Bus for High-Altitude Balloon Missions

### 2017-04-12 chapters/05-discussion.tex
Add byte stuffing to radio

@@

>>>>

Overall, the project could be considered a success. As further section discuss,
some issues were encountered, and most aspects of the \acrshort{ahabus}
platform, protocols and toolchain still require refinement and further testing,
but the results and observation presented in chapter \ref{ch:results} showed
that developing a modular platform for \acrlong{hab} missions based on the
concept of satellite buses is feasible.

@@

The radio protocol and its software implementation proved equally time consuming
and successful. For reasons explained in this section, the protocol could not
be considered final or perfect, but the version developed over the duration of
the project proved reliable enough to transmit large amounts of data over long
simulated test missions.

There were however some observed issues, both in the design of the protocol and
in the frame and packet decoder implementation. First, the current use of a
16-bit unsigned integer to encode the platform's altitude in packet's header
could be problematic even though it did not cause problems during testing: first
because some locations on Earth are located below the mean sea level, leading to
negative altitudes that cannot be encoded with unsigned integers. Then because
the use of 16 bits, while sufficient to encode the altitudes at which balloons
normally fly, leave little to no margin for expansion, for example to
\acrshort{hab}-launched small rockets, or eventually nano-satellites.

Furthermore, it was observed that the reliance on frame length to detect the
end of a frame is error-prone. The current implementation of the frame decoder
counts the 256 bytes that follow a frame start marker as the frame,
unconditionally. As described in section \ref{ssec:results-rtx}, this causes
an issue where dropped bytes in the middle of the frame will cause the start
of the following frame to be consumed as the end of the current one.

One solution to this issue would be the use of an end-of-frame marker instead,
and to reject frames that are shorter than 256 bytes. However, this approach
would be challenging to implement in the context of the \acrshort{ahabus} radio
protocol. Because the end marker value might occur in the frame's content, it
must be escaped so that the decoder does not interpret a content byte as the
frame end. This can be achieved through \textit{byte stuffing}: an escape value
is chosen, and any end marker or escape value that occurs in the content must
be preceded by the escape value. The use of \acrshort{fec} in the protocol
further complicates the issue: the \acrlong{ecc} would have to be escaped too,
making frames impossible to error-correct before the escaped bytes have been
resolved by the decoder. This means that a single corrupted escape byte in a
received frame would prevent the frame from being corrected at all, even if the
number of invalid bytes is inferior to the \acrshort{fec} algorithm limit.
